figures and calculations for global fisheries management

### 2019-01-12 documents/figs-and-calcs.Rmd
need to commit, restarting R

@@

>>>>

projection_data_fig1 <- readRDS(here("data","projection_data.rds")) %>% 
  filter(Scenario == "Historic") %>%
  group_by(IdOrig) %>% 
  filter(Year == max(Year))%>%
  filter(Dbase != "SOFIA") %>%
  filter(IdLevel != "Neis")

projection_data_fig1$CatchShare <- as.factor(projection_data_fig1$CatchShare)

fig_1 = projection_data_fig1 %>%
  ggplot(aes(BvBmsy, FvFmsy, colour = CatchShare, size =MSY, alpha = MSY )) + 
  geom_point() + 
  coord_cartesian(xlim = c(0,3), ylim = c(0,4))+

fig_1

@@

library(sf)
library(ggplot2)
#library(tmap)

projection_data_fig2 <- readRDS(here("data","projection_data.rds")) %>% 
  filter(Scenario == "Historic") %>%
  group_by(IdOrig) %>% 
  filter(Year == max(Year))%>%
  filter(Dbase != "SOFIA") %>%
  filter(IdLevel != "Neis") %>%
  select( IdOrig, Country, CatchShare)

colnames(projection_data_fig2) <- c("IdOrig", "CNTRY_NAME","CatchShare")
projection_data_fig2[projection_data_fig2 =="USA"] <- "United States"

#alreay in 4326; projection = WGS84
countries <- st_read(dsn = "countries_shapefiles", layer = "Countries_WGS84")%>%
  select(CNTRY_NAME)
plot(countries)

projection_spatial <- dplyr::left_join(projection_data_fig2, countries, by = "CNTRY_NAME")
projection_spatial <- st_as_sf(projection_spatial)

fig_2 = ggplot() +
  geom_sf(data= projection_spatial, color = CatchShare)

fig_2
#plot(projection_spatial)

#tm_shape(countries) +
 # tm_polygons() +
  #tm_shape(projection_spatial, colour = CatchShare)
